Implications of afforestation policies for global markets

### 2024-02-28 paper.Rmd
Update paper.Rmd

Table 4. Percentage change in the amount of agricultural exports in 2033, by region, with deforestation mitigation policy in place (Source: GTAP qxw-Ag)
				$\Delta$ (%)
				Agriculture
Japan				8.78
United States			3.49
Canada				3.13
China				1.96
Oceania				1.67
Russia				1.52
West & Central Europe 		1.16
Brazil				1.03
Rest of South America		-2.67
Sub-Saharan Africa		0.02
North Africa & the Middle East	-1.52
Central America			-5.02
Southeast Asia			-5.14
South Asia			-5.94
East Asia			-14.45

Overall, this tax policy, which results in zero net deforestation globally, has a rather significant negative economic impact on all regions except Japan and Canada who see an increase in consumer well-being of $977.1 million and $166.9 million, respectively (Table 5). Consumer well-being is a measurement of equivalent variation and here measures the benefit/harm consumers experience in terms of income as a result of the policy changes. The United States, along with 10 other regions, see well-being drop by more than $1 billion. The most negatively impacted regions are South Asia (-$28.0 billion), China (-$14.5 billion), and Southeast Asia (-$13.6 billion). In total, this tax-driven policy is estimated to decrease global consumer well-being in 2033 by $92.1 billion relative to the scenario where no tax on forestland conversion was in place.

@@

kableExtra::column_spec(
  kableExtra::column_spec(kableExtra::kable_styling(
    knitr::kable(out, caption = 'Change in consumer well-being in 2033, by region, in dollars, with deforestation mitigation policy in place', digits = 1, escape = FALSE, label = 'baseline-scenario1')
  ), 1, border_left = TRUE),
  5,
  border_right = TRUE
)

```
Table 5. Change in consumer well-being in 2033, by region, in dollars, with deforestation mitigation policy in place (Source: GTAP EV) 
				$\Delta$ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
Brazil				-735,125,000
Rest of South America		-3,848,625,000
United States			-1,085,000,000
Russia				-1,152,375,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
West & Central Europe		-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

>>>>

Overall, this tax policy, which results in zero net deforestation globally, has a rather significant negative economic impact on all regions except Japan and Canada who see an increase in consumer well-being of $977.1 million and $166.9 million, respectively (Table \@ref(tab:EV)). Consumer well-being is a measurement of equivalent variation and here measures the benefit/harm consumers experience in terms of income as a result of the policy changes. The United States, along with 10 other regions, see well-being drop by more than $1 billion. The most negatively impacted regions are South Asia (-$28.0 billion), China (-$14.5 billion), and Southeast Asia (-$13.6 billion). In total, this tax-driven policy is estimated to decrease global consumer well-being in 2033 by $92.1 billion relative to the scenario where no tax on forestland conversion was in place.

@@

kableExtra::column_spec(
  kableExtra::column_spec(kableExtra::kable_styling(
    knitr::kable(out, caption = 'Change in consumer well-being in 2033, by region, in dollars, with deforestation mitigation policy in place', digits = 1, escape = FALSE, label = 'EV')
  ), 1, border_left = TRUE),
  5,
  border_right = TRUE
)
